Global Climate and Atmospheric Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and \Spitzer\ Phase Curve Observations

### 2018-04-20 arxiv_v1/ms.tex
arxiv version

\begin{figure}
\includegraphics[width = 0.5\textwidth]{fig1.eps}
%\includegraphics[width = 0.5\textwidth]{fig1-eps-converted-to.pdf}
\caption{$Top$: The normalized nightly Cousins $R$ band photometric dataset for WASP-103, acquired with the C14 automated imaging telescope at Fairborn Observatory. Vertical dashed lines denote separate observing seasons. Gaps are due to target visibility and the Arizona monsoon season (July - September). $Middle$: The frequency spectrum of the normalized dataset suggests low-amplitude variability with a period of 6.814~days. $Bottom$: The normalized dataset phased to the 6.814-day period, which we interpret as rotational modulation of a star spot or spots. A least-squares sine fit to the 6.814-day rotation period gives a peak-to-peak amplitude of just 0.005~mag.}
\label{fig:photometry}
\end{figure}
\begin{deluxetable}{ccccc}
	\tablewidth{0pt}
	\tablecaption{Photometric Observations of WASP-103 \label{tab:photometry}}
	\tablehead{
		\colhead{Observing} & \colhead{$N_{obs}$} & \colhead{Date Range} &
	\colhead{Sigma} & \colhead{Seasonal Mean} \\
	\colhead{Season} &  \colhead{\,} & \colhead{(HJD-2,400,000)} & \colhead{(mag)} & \colhead{(mag)}}
	\startdata
	   2014   &  59 & 56722--56972 & 0.0057 & $0.9546\pm0.0007$  \\
	   2015   &  73 & 57028--57335 & 0.0062 & $0.9549\pm0.0007$  \\
	   2016   &  26 & 57385--57451 & 0.0055 & $0.9485\pm0.0011$  \\
	\enddata
\end{deluxetable}

@@

\bibliographystyle{aasjournal}
\bibliography{ms.bib}

>>>>

\begin{figure}
\includegraphics[width = 0.5\textwidth]{fig1.pdf}
%\includegraphics[width = 0.5\textwidth]{fig1-eps-converted-to.pdf}
\caption{$Top$: The normalized nightly Cousins $R$ band photometric dataset for WASP-103, acquired with the C14 automated imaging telescope at Fairborn Observatory. Vertical dashed lines denote separate observing seasons. Gaps are due to target visibility and the Arizona monsoon season (July - September). $Middle$: The frequency spectrum of the normalized dataset suggests low-amplitude variability with a period of 6.814~days. $Bottom$: The normalized dataset phased to the 6.814-day period, which we interpret as rotational modulation of a star spot or spots. A least-squares sine fit to the 6.814-day rotation period gives a peak-to-peak amplitude of just 0.005~mag.}
\label{fig:photometry}
\end{figure}
\begin{deluxetable}{ccccc}
	\tablewidth{0pt}
	\tablecaption{Photometric Observations of WASP-103 \label{tab:photometry}}
	\tablehead{
		\colhead{Observing} & \colhead{$N_{obs}$} & \colhead{Date Range} &
	\colhead{Sigma} & \colhead{Seasonal Mean} \\
	\colhead{Season} &  \colhead{\,} & \colhead{(HJD-2,400,000)} & \colhead{(mag)} & \colhead{(mag)}}
	\startdata
	   2014   &  59 & 56722--56972 & 0.0057 & $0.9546\pm0.0007$  \\
	   2015   &  73 & 57028--57335 & 0.0062 & $0.9549\pm0.0007$  \\
	   2016   &  26 & 57385--57451 & 0.0055 & $0.9485\pm0.0011$  \\
	\enddata
\end{deluxetable}

@@

 \newcommand{\noop}[1]{}
\begin{thebibliography}{}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
\providecommand{\url}[1]{\href{#1}{#1}}

\bibitem[{Adcroft {et~al.}(2004)Adcroft, Campin, Hill, \&
  Marshall}]{Adcroft2004}
Adcroft, A., Campin, J.-M., Hill, C., \& Marshall, J. 2004, Monthly Weather
  Review, 132, 2845.
\newblock \url{https://doi.org/10.1175/MWR2823.1}

\bibitem[{{Ag{\'u}ndez} {et~al.}(2014){Ag{\'u}ndez}, {Parmentier}, {Venot},
  {Hersant}, \& {Selsis}}]{agundez14}
{Ag{\'u}ndez}, M., {Parmentier}, V., {Venot}, O., {Hersant}, F., \& {Selsis},
  F. 2014, \aap, 564, A73

\bibitem[{{Allard} {et~al.}(2012){Allard}, {Homeier}, \& {Freytag}}]{allard12}
{Allard}, F., {Homeier}, D., \& {Freytag}, B. 2012, Philosophical Transactions
  of the Royal Society of London Series A, 370, 2765

\bibitem[{{Aller} {et~al.}(2013){Aller}, {Kraus}, {Liu}, {Burgett}, {Chambers},
  {Hodapp}, {Kaiser}, {Magnier}, \& {Price}}]{aller13}
{Aller}, K.~M., {Kraus}, A.~L., {Liu}, M.~C., {et~al.} 2013, \apj, 773, 63

\bibitem[{{Arcangeli} {et~al.}(2018){Arcangeli}, {Desert}, {Line}, {Bean},
  {Parmentier}, {Stevenson}, {Kreidberg}, {Fortney}, {Mansfield}, \&
  {Showman}}]{arcangeli18}
{Arcangeli}, J., {Desert}, J.-M., {Line}, M.~R., {et~al.} 2018, ArXiv e-prints,
  arXiv:1801.02489

\bibitem[{{Armstrong} {et~al.}(2016){Armstrong}, {de Mooij}, {Barstow},
  {Osborn}, {Blake}, \& {Saniee}}]{armstrong16}
{Armstrong}, D.~J., {de Mooij}, E., {Barstow}, J., {et~al.} 2016, Nature
  Astronomy, 1, 0004

\bibitem[{{Bagenal} {et~al.}(2004){Bagenal}, {Dowling}, \&
  {McKinnon}}]{bagenal04}
{Bagenal}, F., {Dowling}, T.~E., \& {McKinnon}, W.~B. 2004, {Jupiter : the
  planet, satellites and magnetosphere}

\bibitem[{{Bardalez Gagliuffi} {et~al.}(2014){Bardalez Gagliuffi}, {Burgasser},
  {Gelino}, {Looper}, {Nicholls}, {Schmidt}, {Cruz}, {West}, {Gizis}, \&
  {Metchev}}]{bardalez14}
{Bardalez Gagliuffi}, D.~C., {Burgasser}, A.~J., {Gelino}, C.~R., {et~al.}
  2014, \apj, 794, 143

\bibitem[{{Batygin} {et~al.}(2013){Batygin}, {Stanley}, \&
  {Stevenson}}]{batygin13}
{Batygin}, K., {Stanley}, S., \& {Stevenson}, D.~J. 2013, \apj, 776, 53

\bibitem[{{Beatty} {et~al.}(2017{\natexlab{a}}){Beatty}, {Madhusudhan},
  {Pogge}, {Chung}, {Bierlya}, {Gaudi}, \& {Latham}}]{beatty17a}
{Beatty}, T.~G., {Madhusudhan}, N., {Pogge}, R., {et~al.} 2017{\natexlab{a}},
  \aj, 154, 242

\bibitem[{{Beatty} {et~al.}(2017{\natexlab{b}}){Beatty}, {Madhusudhan},
  {Tsiaras}, {Zhao}, {Gilliland}, {Knutson}, {Shporer}, \&
  {Wright}}]{beatty17b}
{Beatty}, T.~G., {Madhusudhan}, N., {Tsiaras}, A., {et~al.} 2017{\natexlab{b}},
  \aj, 154, 158

\bibitem[{{Bell} \& {Cowan}(2018)}]{bell18}
{Bell}, T.~J., \& {Cowan}, N.~B. 2018, ArXiv e-prints, arXiv:1802.07725

\bibitem[{{Blecic} {et~al.}(2013){Blecic}, {Harrington}, {Madhusudhan},
  {Stevenson}, {Hardy}, {Blecic}, {Anderson}, {Hardin}, \&
  {Campo}}]{Blecic2013}
{Blecic}, J., {Harrington}, J., {Madhusudhan}, N., {et~al.} 2013, \apj, 779, 5

\bibitem[{{Blecic} {et~al.}(2014){Blecic}, {Harrington}, {Madhusudhan},
  {Stevenson}, {Hardy}, {Cubillos}, {Hardin}, {Bowman}, {Nymeyer}, {Anderson},
  {Hellier}, {Smith}, \& {Collier Cameron}}]{Blecic2014}
---. 2014, \apj, 781, 116

\bibitem[{{Bonnefoy} {et~al.}(2014){Bonnefoy}, {Chauvin}, {Lagrange}, {Rojo},
  {Allard}, {Pinte}, {Dumas}, \& {Homeier}}]{bonnefoy14}
{Bonnefoy}, M., {Chauvin}, G., {Lagrange}, A.-M., {et~al.} 2014, \aap, 562,
  A127

\bibitem[{{Bonnefoy} {et~al.}(2009){Bonnefoy}, {Chauvin}, {Dumas}, {Lagrange},
  {Beust}, {Desort}, {Teixeira}, {Ducourant}, {Beuzit}, \& {Song}}]{bonnefoy09}
{Bonnefoy}, M., {Chauvin}, G., {Dumas}, C., {et~al.} 2009, \aap, 506, 799

\bibitem[{{Borucki} {et~al.}(2009){Borucki}, {Koch}, {Jenkins}, {Sasselov},
  {Gilliland}, {Batalha}, {Latham}, {Caldwell}, {Basri}, {Brown},
  {Christensen-Dalsgaard}, {Cochran}, {DeVore}, {Dunham}, {Dupree}, {Gautier},
  {Geary}, {Gould}, {Howell}, {Kjeldsen}, {Lissauer}, {Marcy}, {Meibom},
  {Morrison}, \& {Tarter}}]{borucki09}
{Borucki}, W.~J., {Koch}, D., {Jenkins}, J., {et~al.} 2009, Science, 325, 709

\bibitem[{Braak(2006)}]{braak06}
Braak, C. J. F.~T. 2006, Statistics and Computing, 16, 239.
\newblock \url{http://dx.doi.org/10.1007/s11222-006-8769-1}

\bibitem[{{Campo} {et~al.}(2011){Campo}, {Harrington}, {Hardy}, {Stevenson},
  {et~al.}}]{Campo2011}
{Campo}, C.~J., {Harrington}, J., {Hardy}, R.~A., {Stevenson}, K.~B., {et~al.}
  2011, \apj, 727, 125

\bibitem[{{Carter} \& {Winn}(2009)}]{carter09}
{Carter}, J.~A., \& {Winn}, J.~N. 2009, \apj, 704, 51

\bibitem[{{Cartier} {et~al.}(2017){Cartier}, {Beatty}, {Zhao}, {Line}, {Ngo},
  {Mawet}, {Stassun}, {Wright}, {Kreidberg}, {Fortney}, \&
  {Knutson}}]{cartier17}
{Cartier}, K.~M.~S., {Beatty}, T.~G., {Zhao}, M., {et~al.} 2017, \aj, 153, 34

\bibitem[{{Cowan} \& {Agol}(2008)}]{cowan08}
{Cowan}, N.~B., \& {Agol}, E. 2008, \apjl, 678, L129

\bibitem[{{Cowan} \& {Fujii}(2017)}]{cowan17}
{Cowan}, N.~B., \& {Fujii}, Y. 2017, ArXiv e-prints, arXiv:1704.07832

\bibitem[{{Crossfield} {et~al.}(2012){Crossfield}, {Barman}, {Hansen},
  {Tanaka}, \& {Kodama}}]{crossfield12}
{Crossfield}, I.~J.~M., {Barman}, T., {Hansen}, B.~M.~S., {Tanaka}, I., \&
  {Kodama}, T. 2012, \apj, 760, 140

\bibitem[{{Cruz} {et~al.}(2018){Cruz}, {N{\'u}{\~n}ez}, {Burgasser},
  {Abrahams}, {Rice}, {Reid}, \& {Looper}}]{2018AJ....155...34C}
{Cruz}, K.~L., {N{\'u}{\~n}ez}, A., {Burgasser}, A.~J., {et~al.} 2018, \aj,
  155, 34

\bibitem[{{Cruz} {et~al.}(2007){Cruz}, {Reid}, {Kirkpatrick}, {Burgasser},
  {Liebert}, {Solomon}, {Schmidt}, {Allen}, {Hawley}, \&
  {Covey}}]{2007AJ....133..439C}
{Cruz}, K.~L., {Reid}, I.~N., {Kirkpatrick}, J.~D., {et~al.} 2007, \aj, 133,
  439

\bibitem[{{Cubillos} {et~al.}(2013){Cubillos}, {Harrington}, {Madhusudhan},
  {Stevenson}, {Hardy}, {Blecic}, {Anderson}, {Hardin}, \&
  {Campo}}]{cubillos13}
{Cubillos}, P., {Harrington}, J., {Madhusudhan}, N., {et~al.} 2013, \apj, 768,
  42

\bibitem[{{de Wit} {et~al.}(2012){de Wit}, {Gillon}, {Demory}, \&
  {Seager}}]{dewit12}
{de Wit}, J., {Gillon}, M., {Demory}, B.-O., \& {Seager}, S. 2012, \aap, 548,
  A128

\bibitem[{{Delrez} {et~al.}(2018){Delrez}, {Madhusudhan}, {Lendl}, {Gillon},
  {Anderson}, {Neveu-VanMalle}, {Bouchy}, {Burdanov}, {Collier-Cameron},
  {Demory}, {Hellier}, {Jehin}, {Magain}, {Maxted}, {Queloz}, {Smalley}, \&
  {Triaud}}]{delrez18}
{Delrez}, L., {Madhusudhan}, N., {Lendl}, M., {et~al.} 2018, \mnras, 474, 2334

\bibitem[{{Demory} {et~al.}(2013){Demory}, {de Wit}, {Lewis}, {Fortney},
  {Zsom}, {Seager}, {Knutson}, {Heng}, {Madhusudhan}, {Gillon}, {Barclay},
  {Desert}, {Parmentier}, \& {Cowan}}]{demory13}
{Demory}, B.-O., {de Wit}, J., {Lewis}, N., {et~al.} 2013, \apjl, 776, L25

\bibitem[{{Diamond-Lowe} {et~al.}(2014{\natexlab{a}}){Diamond-Lowe},
  {Stevenson}, {Bean}, {Line}, \& {Fortney}}]{HDL2014}
{Diamond-Lowe}, H., {Stevenson}, K.~B., {Bean}, J.~L., {Line}, M.~R., \&
  {Fortney}, J.~J. 2014{\natexlab{a}}, \apj, 796, 66

\bibitem[{{Diamond-Lowe} {et~al.}(2014{\natexlab{b}}){Diamond-Lowe},
  {Stevenson}, {Bean}, {Line}, \& {Fortney}}]{diamond-lowe14}
---. 2014{\natexlab{b}}, \apj, 796, 66

\bibitem[{{Dieterich} {et~al.}(2014){Dieterich}, {Henry}, {Jao}, {Winters},
  {Hosey}, {Riedel}, \& {Subasavage}}]{2014AJ....147...94D}
{Dieterich}, S.~B., {Henry}, T.~J., {Jao}, W.-C., {et~al.} 2014, \aj, 147, 94

\bibitem[{{Espinoza} {et~al.}(2017){Espinoza}, {Fortney}, {Miguel},
  {Thorngren}, \& {Murray-Clay}}]{espinoza17}
{Espinoza}, N., {Fortney}, J.~J., {Miguel}, Y., {Thorngren}, D., \&
  {Murray-Clay}, R. 2017, \apjl, 838, L9

\bibitem[{{Evans} {et~al.}(2016){Evans}, {Sing}, {Wakeford}, {Nikolov},
  {Ballester}, {Drummond}, {Kataria}, {Gibson}, {Amundsen}, \&
  {Spake}}]{evans16}
{Evans}, T.~M., {Sing}, D.~K., {Wakeford}, H.~R., {et~al.} 2016, \apjl, 822, L4

\bibitem[{{Faherty} {et~al.}(2010){Faherty}, {Burgasser}, {West}, {Bochanski},
  {Cruz}, {Shara}, \& {Walter}}]{2010AJ....139..176F}
{Faherty}, J.~K., {Burgasser}, A.~J., {West}, A.~A., {et~al.} 2010, \aj, 139,
  176

\bibitem[{{Faherty} {et~al.}(2012){Faherty}, {Burgasser}, {Walter}, {Van der
  Bliek}, {Shara}, {Cruz}, {West}, {Vrba}, \&
  {Anglada-Escud{\'e}}}]{2012ApJ...752...56F}
{Faherty}, J.~K., {Burgasser}, A.~J., {Walter}, F.~M., {et~al.} 2012, \apj,
  752, 56

\bibitem[{{Faherty} {et~al.}(2016){Faherty}, {Riedel}, {Cruz}, {Gagne},
  {Filippazzo}, {Lambrides}, {Fica}, {Weinberger}, {Thorstensen}, {Tinney},
  {Baldassare}, {Lemonier}, \& {Rice}}]{faherty16}
{Faherty}, J.~K., {Riedel}, A.~R., {Cruz}, K.~L., {et~al.} 2016, \apjs, 225, 10

\bibitem[{{Filippazzo} {et~al.}(2015){Filippazzo}, {Rice}, {Faherty}, {Cruz},
  {Van Gordon}, \& {Looper}}]{filippazzo15}
{Filippazzo}, J.~C., {Rice}, E.~L., {Faherty}, J., {et~al.} 2015, \apj, 810,
  158

\bibitem[{{Foreman-Mackey} {et~al.}(2013){Foreman-Mackey}, {Hogg}, {Lang}, \&
  {Goodman}}]{foremanmackey13}
{Foreman-Mackey}, D., {Hogg}, D.~W., {Lang}, D., \& {Goodman}, J. 2013, \pasp,
  125, 306

\bibitem[{{Fortney} {et~al.}(2008){Fortney}, {Lodders}, {Marley}, \&
  {Freedman}}]{fortney08}
{Fortney}, J.~J., {Lodders}, K., {Marley}, M.~S., \& {Freedman}, R.~S. 2008,
  \apj, 678, 1419

\bibitem[{{Fortney} {et~al.}(2013){Fortney}, {Mordasini}, {Nettelmann},
  {Kempton}, {Greene}, \& {Zahnle}}]{fortney13}
{Fortney}, J.~J., {Mordasini}, C., {Nettelmann}, N., {et~al.} 2013, \apj, 775,
  80

\bibitem[{{Freedman} {et~al.}(2014){Freedman}, {Lustig-Yaeger}, {Fortney},
  {Lupu}, {Marley}, \& {Lodders}}]{freedman14}
{Freedman}, R.~S., {Lustig-Yaeger}, J., {Fortney}, J.~J., {et~al.} 2014, \apjs,
  214, 25

\bibitem[{{Gaia Collaboration} {et~al.}(2016){Gaia Collaboration}, {Prusti},
  {de Bruijne}, {Brown}, {Vallenari}, {Babusiaux}, {Bailer-Jones}, {Bastian},
  {Biermann}, {Evans}, \& et~al.}]{gaia16}
{Gaia Collaboration}, {Prusti}, T., {de Bruijne}, J.~H.~J., {et~al.} 2016,
  \aap, 595, A1

\bibitem[{{Geballe} {et~al.}(2002){Geballe}, {Knapp}, {Leggett}, {Fan},
  {Golimowski}, {Anderson}, {Brinkmann}, {Csabai}, {Gunn}, {Hawley},
  {Hennessy}, {Henry}, {Hill}, {Hindsley}, {Ivezi{\'c}}, {Lupton}, {McDaniel},
  {Munn}, {Narayanan}, {Peng}, {Pier}, {Rockosi}, {Schneider}, {Smith},
  {Strauss}, {Tsvetanov}, {Uomoto}, {York}, \& {Zheng}}]{geballe02}
{Geballe}, T.~R., {Knapp}, G.~R., {Leggett}, S.~K., {et~al.} 2002, \apj, 564,
  466

\bibitem[{{Gillon} {et~al.}(2014){Gillon}, {Anderson}, {Collier-Cameron},
  {Delrez}, {Hellier}, {Jehin}, {Lendl}, {Maxted}, {Pepe}, {Pollacco},
  {Queloz}, {S{\'e}gransan}, {Smith}, {Smalley}, {Southworth}, {Triaud},
  {Udry}, {Van Grootel}, \& {West}}]{gillon14}
{Gillon}, M., {Anderson}, D.~R., {Collier-Cameron}, A., {et~al.} 2014, \aap,
  562, L3

\bibitem[{Gordon \& McBride(1994)}]{gordon94}
Gordon, S., \& McBride, B.~J. 1994, Computer program for calculation of complex
  chemical equilibrium compositions and applications, Vol.~1 (National
  Aeronautics and Space Administration, Office of Management, Scientific and
  Technical Information Program)

\bibitem[{{Grie{\ss}meier}(2015)}]{griessmeier15}
{Grie{\ss}meier}, J.-M. 2015, in Astrophysics and Space Science Library, Vol.
  411, Characterizing Stellar and Exoplanetary Environments, ed. H.~{Lammer} \&
  M.~{Khodachenko}, 213

\bibitem[{{Harrington} {et~al.}(2006){Harrington}, {Hansen}, {Luszcz},
  {Seager}, {Deming}, {Menou}, {Cho}, \& {Richardson}}]{harrington06}
{Harrington}, J., {Hansen}, B.~M., {Luszcz}, S.~H., {et~al.} 2006, Science,
  314, 623

\bibitem[{{Harrington} {et~al.}(2007){Harrington}, {Luszcz}, {Seager},
  {Deming}, \& {Richardson}}]{Harrington2007}
{Harrington}, J., {Luszcz}, S., {Seager}, S., {Deming}, D., \& {Richardson},
  L.~J. 2007, Nature, 447, 691

\bibitem[{{Hayes}(1985)}]{1985IAUS..111..225H}
{Hayes}, D.~S. 1985, in IAU Symposium, Vol. 111, Calibration of Fundamental
  Stellar Quantities, ed. D.~S. {Hayes}, L.~E. {Pasinetti}, \& A.~G.~D.
  {Philip}, 225--249

\bibitem[{{Haynes} {et~al.}(2015){Haynes}, {Mandell}, {Madhusudhan}, {Deming},
  \& {Knutson}}]{haynes15}
{Haynes}, K., {Mandell}, A.~M., {Madhusudhan}, N., {Deming}, D., \& {Knutson},
  H. 2015, \apj, 806, 146

\bibitem[{{Henry}(1999)}]{henry99}
{Henry}, G.~W. 1999, \pasp, 111, 845

\bibitem[{{Horne}(1986)}]{horne86}
{Horne}, K. 1986, \pasp, 98, 609

\bibitem[{{Hu} {et~al.}(2015){Hu}, {Demory}, {Seager}, {Lewis}, \&
  {Showman}}]{hu15}
{Hu}, R., {Demory}, B.-O., {Seager}, S., {Lewis}, N., \& {Showman}, A.~P. 2015,
  \apj, 802, 51

\bibitem[{{Hubeny} {et~al.}(2003){Hubeny}, {Burrows}, \& {Sudarsky}}]{hubeny03}
{Hubeny}, I., {Burrows}, A., \& {Sudarsky}, D. 2003, \apj, 594, 1011

\bibitem[{{Ingalls} {et~al.}(2016){Ingalls}, {Krick}, {Carey}, {Stauffer},
  {Lowrance}, {Grillmair}, {Buzasi}, {Deming}, {Diamond-Lowe}, {Evans},
  {Morello}, {Stevenson}, {Wong}, {Capak}, {Glaccum}, {Laine}, {Surace}, \&
  {Storrie-Lombardi}}]{Ingalls2016}
{Ingalls}, J.~G., {Krick}, J.~E., {Carey}, S.~J., {et~al.} 2016, \aj, 152, 44

\bibitem[{Jones {et~al.}(2001)Jones, Oliphant, Peterson, \&
  Others}]{jones_scipy_2001}
Jones, E., Oliphant, T., Peterson, P., \& Others. 2001, {SciPy}: Open source
  scientific tools for Python, , .
\newblock \url{http://www.scipy.org/}

\bibitem[{Kass \& Raftery(1995)}]{kass95}
Kass, R.~E., \& Raftery, A.~E. 1995, Journal of the American Statistical
  Association, 90, 773.
\newblock
  \url{http://amstat.tandfonline.com/doi/abs/10.1080/01621459.1995.10476572}

\bibitem[{{Kataria} {et~al.}(2016){Kataria}, {Sing}, {Lewis}, {Visscher},
  {Showman}, {Fortney}, \& {Marley}}]{kataria16}
{Kataria}, T., {Sing}, D.~K., {Lewis}, N.~K., {et~al.} 2016, \apj, 821, 9

\bibitem[{{Kendall} {et~al.}(2003){Kendall}, {Mauron}, {Azzopardi}, \&
  {Gigoyan}}]{2003A&A...403..929K}
{Kendall}, T.~R., {Mauron}, N., {Azzopardi}, M., \& {Gigoyan}, K. 2003, \aap,
  403, 929

\bibitem[{{Kirkpatrick} {et~al.}(1993){Kirkpatrick}, {Kelly}, {Rieke},
  {Liebert}, {Allard}, \& {Wehrse}}]{kirkpatrick93}
{Kirkpatrick}, J.~D., {Kelly}, D.~M., {Rieke}, G.~H., {et~al.} 1993, \apj, 402,
  643

\bibitem[{{Koll} \& {Komacek}(2018)}]{koll18}
{Koll}, D.~D.~B., \& {Komacek}, T.~D. 2018, \apj, 853, 133

\bibitem[{{Komacek} \& {Showman}(2016)}]{komacek16}
{Komacek}, T.~D., \& {Showman}, A.~P. 2016, \apj, 821, 16

\bibitem[{{Komacek} {et~al.}(2017){Komacek}, {Showman}, \& {Tan}}]{komacek17}
{Komacek}, T.~D., {Showman}, A.~P., \& {Tan}, X. 2017, \apj, 835, 198

\bibitem[{{Kreidberg}(2015)}]{kreidberg15a}
{Kreidberg}, L. 2015, \pasp, 127, 1161

\bibitem[{{Kreidberg} {et~al.}(2014{\natexlab{a}}){Kreidberg}, {Bean},
  {D{\'e}sert}, {Benneke}, {Deming}, {Stevenson}, {Seager}, {Berta-Thompson},
  {Seifahrt}, \& {Homeier}}]{kreidberg14a}
{Kreidberg}, L., {Bean}, J.~L., {D{\'e}sert}, J.-M., {et~al.}
  2014{\natexlab{a}}, \nat, 505, 69

\bibitem[{{Kreidberg} {et~al.}(2014{\natexlab{b}}){Kreidberg}, {Bean},
  {D{\'e}sert}, {Line}, {Fortney}, {Madhusudhan}, {Stevenson}, {Showman},
  {Charbonneau}, {McCullough}, {Seager}, {Burrows}, {Henry}, {Williamson},
  {Kataria}, \& {Homeier}}]{kreidberg14b}
---. 2014{\natexlab{b}}, \apjl, 793, L27

\bibitem[{{Kreidberg} {et~al.}(2015){Kreidberg}, {Line}, {Bean}, {Stevenson},
  {D{\'e}sert}, {Madhusudhan}, {Fortney}, {Barstow}, {Henry}, {Williamson}, \&
  {Showman}}]{kreidberg15b}
{Kreidberg}, L., {Line}, M.~R., {Bean}, J.~L., {et~al.} 2015, \apj, 814, 66

\bibitem[{{Leconte} {et~al.}(2011{\natexlab{a}}){Leconte}, {Lai}, \&
  {Chabrier}}]{leconte11b}
{Leconte}, J., {Lai}, D., \& {Chabrier}, G. 2011{\natexlab{a}}, \aap, 536, C1

\bibitem[{{Leconte} {et~al.}(2011{\natexlab{b}}){Leconte}, {Lai}, \&
  {Chabrier}}]{leconte11a}
---. 2011{\natexlab{b}}, \aap, 528, A41

\bibitem[{{Lendl} {et~al.}(2017){Lendl}, {Cubillos}, {Hagelberg}, {M{\"u}ller},
  {Juvan}, \& {Fossati}}]{lendl17}
{Lendl}, M., {Cubillos}, P.~E., {Hagelberg}, J., {et~al.} 2017, \aap, 606, A18

\bibitem[{{Line} {et~al.}(2014){Line}, {Knutson}, {Wolf}, \& {Yung}}]{line14}
{Line}, M.~R., {Knutson}, H., {Wolf}, A.~S., \& {Yung}, Y.~L. 2014, \apj, 783,
  70

\bibitem[{{Line} {et~al.}(2013){Line}, {Wolf}, {Zhang}, {Knutson}, {Kammer},
  {Ellison}, {Deroo}, {Crisp}, \& {Yung}}]{line13a}
{Line}, M.~R., {Wolf}, A.~S., {Zhang}, X., {et~al.} 2013, \apj, 775, 137

\bibitem[{{Line} {et~al.}(2016){Line}, {Stevenson}, {Bean}, {Desert},
  {Fortney}, {Kreidberg}, {Madhusudhan}, {Showman}, \& {Diamond-Lowe}}]{line16}
{Line}, M.~R., {Stevenson}, K.~B., {Bean}, J., {et~al.} 2016, \aj, 152, 203

\bibitem[{{Lodders} \& {Fegley}(2002)}]{Lodders2002a}
{Lodders}, K., \& {Fegley}, B. 2002, \icarus, 155, 393

\bibitem[{{Loeb} \& {Gaudi}(2003)}]{loeb03}
{Loeb}, A., \& {Gaudi}, B.~S. 2003, \apjl, 588, L117

\bibitem[{{Long} {et~al.}(2015){Long}, {Baggett}, \& {MacKenty}}]{long15}
{Long}, K.~S., {Baggett}, S.~M., \& {MacKenty}, J.~W. 2015, {Persistence in the
  WFC3 IR Detector: an Improved Model Incorporating the Effects of Exposure
  Time}, Tech. rep.

\bibitem[{{Louden} \& {Kreidberg}(2017)}]{louden17}
{Louden}, T., \& {Kreidberg}, L. 2017, ArXiv e-prints, arXiv:1711.00494

\bibitem[{{Lust} {et~al.}(2014){Lust}, {Britt}, {Harrington}, {Nymeyer},
  {Stevenson}, {Ross}, {Bowman}, \& {Fraine}}]{Lust2014}
{Lust}, N.~B., {Britt}, D., {Harrington}, J., {et~al.} 2014, \pasp, 126, 1092

\bibitem[{{Madhusudhan} {et~al.}(2011){Madhusudhan}, {Harrington}, {Stevenson},
  {Nymeyer}, {Campo}, {Wheatley}, {Deming}, {Blecic}, {Hardy}, {Lust},
  {Anderson}, {Collier-Cameron}, {Britt}, {Bowman}, {Hebb}, {Hellier},
  {Maxted}, {Pollacco}, \& {West}}]{madhusudhan11}
{Madhusudhan}, N., {Harrington}, J., {Stevenson}, K.~B., {et~al.} 2011, \nat,
  469, 64

\bibitem[{{Mansfield} {et~al.}(\noop{3001}submitted){Mansfield}, {Bean},
  {Line}, {Paramentier}, \& {Kreidberg}}]{mansfield18}
{Mansfield}, M., {Bean}, J.~B., {Line}, M., {Paramentier}, V., \& {Kreidberg},
  L. \noop{3001}submitted, Submitted to \apj

\bibitem[{{Marley} \& {McKay}(1999)}]{Marley1999}
{Marley}, M.~S., \& {McKay}, C.~P. 1999, \icarus, 138, 268

\bibitem[{{McCullough} \& {MacKenty}(2012)}]{mccullough12}
{McCullough}, P., \& {MacKenty}, J. 2012, {Considerations for using Spatial
  Scans with WFC3}, Tech. rep.

\bibitem[{{McLean} {et~al.}(2003){McLean}, {McGovern}, {Burgasser},
  {Kirkpatrick}, {Prato}, \& {Kim}}]{mclean03}
{McLean}, I.~S., {McGovern}, M.~R., {Burgasser}, A.~J., {et~al.} 2003, \apj,
  596, 561

\bibitem[{{Mordasini} {et~al.}(2016){Mordasini}, {van Boekel}, {Molli{\`e}re},
  {Henning}, \& {Benneke}}]{mordasini16}
{Mordasini}, C., {van Boekel}, R., {Molli{\`e}re}, P., {Henning}, T., \&
  {Benneke}, B. 2016, \apj, 832, 41

\bibitem[{{Mountain} {et~al.}(1985){Mountain}, {Selby}, {Leggett}, {Blackwell},
  \& {Petford}}]{1985A&A...151..399M}
{Mountain}, C.~M., {Selby}, M.~J., {Leggett}, S.~K., {Blackwell}, D.~E., \&
  {Petford}, A.~D. 1985, \aap, 151, 399

\bibitem[{{Nymeyer} {et~al.}(2011){Nymeyer}, {Harrington}, {Hardy}, {\bfseries
  {Stevenson}, K.~B.}, {Campo}, {Madhusudhan}, {Collier-Cameron}, {Loredo},
  {Blecic}, {Bowman}, {Britt}, {Cubillos}, {Hellier}, {Gillon}, {Maxted},
  {Hebb}, {Wheatley}, {Pollacco}, \& {Anderson}}]{Nymeyer2011}
{Nymeyer}, S., {Harrington}, J., {Hardy}, R.~A., {et~al.} 2011, ApJ, 742, 35

\bibitem[{{Parmentier} \& {Crossfield}(2017)}]{parmentier17}
{Parmentier}, V., \& {Crossfield}, I. 2017, ArXiv e-prints, arXiv:1711.07696

\bibitem[{{Parmentier} {et~al.}(2016){Parmentier}, {Fortney}, {Showman},
  {Morley}, \& {Marley}}]{parmentier16}
{Parmentier}, V., {Fortney}, J.~J., {Showman}, A.~P., {Morley}, C., \&
  {Marley}, M.~S. 2016, \apj, 828, 22

\bibitem[{{Parmentier} {et~al.}(\noop{3001}submitted){Parmentier}, {Line},
  {Bean}, {Fortney}, {D\'{e}sert}, \& {Kreidberg}}]{parmentier18}
{Parmentier}, V., {Line}, M.~R., {Bean}, J., {et~al.} \noop{3001}submitted,
  Submitted to A\&A

\bibitem[{{Perez-Becker} \& {Showman}(2013)}]{perez13}
{Perez-Becker}, D., \& {Showman}, A.~P. 2013, \apj, 776, 134

\bibitem[{{Perna} {et~al.}(2010){Perna}, {Menou}, \& {Rauscher}}]{perna10}
{Perna}, R., {Menou}, K., \& {Rauscher}, E. 2010, \apj, 719, 1421

\bibitem[{{Pont} {et~al.}(2006){Pont}, {Zucker}, \& {Queloz}}]{pont06}
{Pont}, F., {Zucker}, S., \& {Queloz}, D. 2006, \mnras, 373, 231

\bibitem[{{Reid} {et~al.}(2001){Reid}, {Burgasser}, {Cruz}, {Kirkpatrick}, \&
  {Gizis}}]{reid01}
{Reid}, I.~N., {Burgasser}, A.~J., {Cruz}, K.~L., {Kirkpatrick}, J.~D., \&
  {Gizis}, J.~E. 2001, \aj, 121, 1710

\bibitem[{{Reid} {et~al.}(2008){Reid}, {Cruz}, {Kirkpatrick}, {Allen},
  {Mungall}, {Liebert}, {Lowrance}, \& {Sweet}}]{reid08}
{Reid}, I.~N., {Cruz}, K.~L., {Kirkpatrick}, J.~D., {et~al.} 2008, \aj, 136,
  1290

\bibitem[{{Rogers}(2017)}]{rogers17}
{Rogers}, T.~M. 2017, Nature Astronomy, 1, 0131

\bibitem[{{Rogers} \& {Komacek}(2014)}]{rogers14a}
{Rogers}, T.~M., \& {Komacek}, T.~D. 2014, \apj, 794, 132

\bibitem[{{Rogers} \& {Showman}(2014)}]{rogers14}
{Rogers}, T.~M., \& {Showman}, A.~P. 2014, \apjl, 782, L4
